---
title: "Project 4"
output:
  html_document:
    toc: yes
    toc_depth: '3'
    df_print: paged
  html_notebook:
    pandoc_args: --number-offset=1,0
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
---

```{r}
library(tm)
library(caTools)
sh = read.csv("spam_ham_dataset.csv")
```
After loading the data set into R, we will look at its structure
```{r}
head(sh)
str(sh)
```

Now, let's check how many are labeled as 'spam' and 'not-spam'
```{r}
table(sh$label_num)
```

Now, let's create the corpus and clean the text:
Convert into lower, remove punctuation, and remove stop words.
Turn into a Document Term Matrix, called "doc_tm"
```{r}
corpus = VCorpus(VectorSource(sh$text))
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, PlainTextDocument)
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, removeWords, stopwords("en"))
doc_tm = DocumentTermMatrix(corpus)
doc_tm
```
Now let's remove the sparse terms in the matrix and create a data frame, called "sh1"

```{r}
rem = removeSparseTerms(doc_tm, 0.85)
rem
```

```{r}
sh1 = as.data.frame(as.matrix(rem))
```

Now, we will use the 'colSums' function to see the frequency of each word in the data set
```{r}
colnames(colSums(sh1))
sort(colSums(sh1))
```


```{r}
sh1$spam = sh$label_num
sort(colSums(subset(sh1, "label_num" == 0)))
sort(colSums(subset(sh1, "label_num" == 1)))
```
```{r}
sh1$spam = as.factor(sh1$spam)
```

Now, let's see the accuracy of the data adn create a subset of the spam model, and a subset of the non-spam model
```{r}
set.seed(123)
split = sample.split(sh1$spam, .8)
train_set = subset(sh1, split == TRUE)
test_set = subset(sh1, split == FALSE)
spams = glm(spam~., data = train_set, family = "binomial")
```


Now, for some predictions

```{r}
pred = predict(spams, type = "response")
table(train_set$spam, pred > 0.5)
```

```{r}
accuracy1 = (2571+1082)/nrow(train_set)
```

```{r}
pred2 = predict(spams, newdata = test_set, type = "response")
table(test_set$spam, pred2 > 0.5)
```

```{r}
accuracy2 = (662+278)/nrow(test_set)
```

```{r}
accuracy1
accuracy2
```

This shows that the accuracy is around 90%.
